\begin{document}

%====================
% EXPERIENCE A
%====================

\hspace{1em}


\begin{zitemize}
\item{Procédé Multiparamétrique de Quantification de l’Equilibre , 2016, reference FR1660846}
\item{Postural Control quantification and evaluation, US Patent US Patent App. 16/346,395 }
\item{Improved method for quantifying balance , 2020, reference US Patent App. 16/763,573}
\item{System and Method for Predicting Depth of Anesthesia , 2021, reference EU Patent App.
(pending) 0757-IDF38-EP}
\end{zitemize}



\iffalse
\section{Five Selected publications}


\begin{zitemize}
    \item Audiffren, J.. (2021).  \href{https://proceedings.mlr.press/v139/audiffren21a.html.}{Dichotomous Optimistic Search to Quantify Human Perception.} Proceedings of the 38th International Conference on Machine Learning, in Proceedings of Machine Learning Research 139:414-424.
    \item Kadri, H., Duflos, E., Preux, P., Canu, S., Rakotomamonjy, A., \& Audiffren, J. (2016). \href{https://www.jmlr.org/papers/volume17/11-315/11-315.pdf}{Operator-valued kernels for learning from functional response data}. Journal of Machine Learning Research, 17(20), 1-54.
    \item Audiffren, J., \& Ralaivola, L. (2015). \href{https://proceedings.neurips.cc/paper/2015/file/4888241374e8c62ddd9b4c3cfd091f96-Paper.pdf}{Cornering stationary and restless mixing bandits with remix-ucb}. Advances in Neural Information Processing Systems, 28.
    \item Ostapuk N., Audiffren J. et al. (2024). \href{https://dl.acm.org/doi/pdf/10.1145/3589334.3645558}{Follow the Path: Hierarchy-Aware Extreme Multi-Label Completion for Semantic Text Tagging}. The Web Conf.
    \item Bloechle J.L, Audiffren J. et al. (2024).
    \href{https://www.sciencedirect.com/science/article/pii/S2666675824000225}{It’s not all in your feet: Improving penalty kick performance with human-avatar interaction and machine learning} The Innovation (Cell Press).
\end{zitemize}

\fi



\end{document}